Statement-level AST-based Clone Detection in Java using Resolved Symbols

### 2019-11-06 benevol/main.tex
Updates from Overleaf

\title{Statement-level AST-based Clone Detection in Java using Resolved Symbols}
\author{Simon Baars, Ana Oprescu}
%\affiliation{University of Amsterdam}

@@

\input{introduction}

\input{case}

\input{approaches}

\input{comparison}

\input{analysis}

\input{conclusion}

>>>>

\title{Statement-level AST-based Clone Detection in Java using Resolved Symbols}
\author{Simon Baars, Ana Oprescu}
\affiliation{University of Amsterdam}

@@

\section{Introduction}
Most clone detection tools can be configured using thresholds. These thresholds indicate the minimum number of lines, tokens and/or statements that must be spanned for duplicate fragments to be considered clones. Often, such thresholds are intuitively chosen~\cite{li2006cp, roy2009mutation} or based on a quartile distribution of empirical data~\cite{alves2010deriving}. Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.

\section{Conclusion}
